Region-network hierarchical sparsity priors for\\ high-dimensional inference in brain imaging

### 2016-01-29 paper/paper.tex
pass over abstract

\begin{abstract}
% Imaging neuroscience links human behavior to aspects of brain
% biology in ever-increasing datasets.

\textbf{\\keywords}:
Sparsity-inducing norms, hierarchical structured sparsity,
numerical optimization,
systems neuroscience, brain imaging,
functional specialization, functional integration

>>>>

\begin{abstract}
Structured sparsity penalization has recently improved
statistical models applied to high-dimensional data in various domains.
As an extension to imaging neuroscience,
priors on network hierarchies of brain regions have been incorporated into
logistic-regression estimators for neural activity maps.
This remarries the perspectives of
functional segregation and functional integration
that are routinely divorced in neuroscientific research.
%
Region-network hierarchical priors for supervised classification
of 18 psychological tasks
from a reference dataset are
shown to outperform na\"ive $\ell_1$-norm and
trace-norm penalization, as well as neurobiologically
informed $\ell_1/\ell_2$-block-norm group sparsity.
Varying the relative importance of
region and network structure within the hierarchical tree prior
recovered complementary aspects of the neural activity pattern
with similar predictive accuracies.
%
In sum,
we demonstrate that priors of local and global neurobiological knowledge can enhance
out-of-sample performance and domain interpretability
by hierarchical tree sparsity.

\textbf{\\keywords}:
Sparsity-inducing norms, hierarchical tree sparsity,
numerical optimization,
systems neuroscience,
functional specialization, functional integration
